A meta-analysis of mental rotation ability in the first years of life

### 2022-05-05 code/analysis.Rmd
Fix italics vs. bold

For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects. Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig. 1). The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level. Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm$icc)` was attributable to differences between articles.

@@

To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported within each article by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig. 1) and a probability of this effect being greater than zero of `r print_perc(hyp_brm_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level. Therefore, approximately `r print_perc(1 - summ_brm_gender$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments and `r print_perc(summ_brm_gender$icc)` was attributable to differences between articles.

>>>>

For our first meta-analytic model effect sizes were quantified as the standardized mean difference in infants’ looking times for novel and familiar rotated objects. Using this effect size index we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_brm$intercept`$, 95% credible interval (CrI) [`r summ_brm$intercept.lower`, `r summ_brm$intercept.upper`] (Fig. 1). The probability for this effect being greater than zero was `r print_perc(hyp_brm$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm$sigma2_experiment`$, 95% CrI [`r summ_brm$sigma2_experiment.lower`, `r summ_brm$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm$sigma2_article`$, 95% CrI [`r summ_brm$sigma2_article.lower`, `r summ_brm$sigma2_article.upper`] at the article level. Therefore, approximately `r print_perc(1 - summ_brm$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_brm$icc)` was attributable to differences *between* articles.

@@

To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_brm_gender$intercept`$, 95% Crl [`r summ_brm_gender$intercept.lower`, `r summ_brm_gender$intercept.upper`] (Supplementary Fig. 1) and a probability of this effect being greater than zero of `r print_perc(hyp_brm_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_brm_gender$sigma2_experiment`$, 95% CrI [`r summ_brm_gender$sigma2_experiment.lower`, `r summ_brm_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_brm_gender$sigma2_article`$, 95% CrI [`r summ_brm_gender$sigma2_article.lower`, `r summ_brm_gender$sigma2_article.upper`] at the article level. This means that `r print_perc(summ_brm_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_brm_gender$icc)` to differences between experiments *within* articles.
